---
title: "COVID Survey Structural Equation Modeling April 2021"
date: "4/7/2021"
output: word_document
---
```{r}
library(psych)
library(lavaan)
library(semPlot)
```

#k6
```{r}
modelfig17 <- '
#Serial Mediation, COVID Positive predicting K6 mediating difficulty coping predicting seeking professional healthcare
# Regressions
sph ~ dc + k6 + COVIDP'

```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare
fitfig17 <-lavaan(modelfig4, ordered = c("st", "k6", "ang", "dc", "uis", "sph", "COVIDP", "COVIDH", "COVIDD", "COVIDDH"), bootstrap = TRUE, data = SEM)
```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare 
summary (fitfig17, fit.measures = TRUE, standardized = TRUE)
```

```{r}
modelfig18 <- '
##Serial Mediation, COVID Hospitalized predicting K6 mediating difficulty coping predicting seeking professional healthcare
# Regressions
sph ~ dc + k6 + COVIDH'

```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare
fitfig18 <-lavaan(modelfig18, ordered = c("st", "k6", "ang", "dc", "uis", "sph", "COVIDP", "COVIDH", "COVIDD", "COVIDDH"), bootstrap = TRUE, data = SEM)
```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare 
summary (fitfig18, fit.measures = TRUE, standardized = TRUE)
```

```{r}
modelfig19 <- '
#Serial Mediation, COVID Death predicting K6 mediating difficulty coping predicting seeking professional healthcare
# Regressions
sph ~ dc + k6 + COVIDD'

```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare
fitfig4 <-lavaan(modelfig19, ordered = c("st", "k6", "ang", "dc", "uis", "sph", "COVIDP", "COVIDH", "COVIDD", "COVIDDH"), bootstrap = TRUE, data = SEM)
```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare 
summary (fitfig19, fit.measures = TRUE, standardized = TRUE)
```

```{r}
modelfig20 <- '
#Serial Mediation, COVID Delayed Healthcare predicting K6 mediating difficulty coping predicting seeking professional healthcare
# Regressions
sph ~ dc + k6 + COVIDDH'

```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare
fitfig20 <-lavaan(modelfig20, ordered = c("st", "k6", "ang", "dc", "uis", "sph", "COVIDP", "COVIDH", "COVIDD", "COVIDDH"), bootstrap = TRUE, data = SEM)
```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare 
summary (fitfig20, fit.measures = TRUE, standardized = TRUE)
```

#ANGER
```{r}
modelfig21 <- '
#Serial Mediation, COVID Positive predicting anger mediating difficulty coping predicting seeking professional healthcare
# Regressions
sph ~ dc + ang + COVIDP'

```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare
fitfig21 <-lavaan(modelfig21, ordered = c("st", "k6", "ang", "dc", "uis", "sph", "COVIDP", "COVIDH", "COVIDD", "COVIDDH"), bootstrap = TRUE, data = SEM)
```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare 
summary (fitfig21, fit.measures = TRUE, standardized = TRUE)
```

```{r}
modelfig22 <- '
##Serial Mediation, COVID Hospitalized predicting anger mediating difficulty coping predicting seeking professional healthcare
# Regressions
sph ~ dc + ang + COVIDH'

```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare
fitfig22 <-lavaan(modelfig22, ordered = c("st", "k6", "ang", "dc", "uis", "sph", "COVIDP", "COVIDH", "COVIDD", "COVIDDH"), bootstrap = TRUE, data = SEM)
```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare 
summary (fitfig22, fit.measures = TRUE, standardized = TRUE)
```

```{r}
modelfig23 <- '
#Serial Mediation, COVID Death predicting anger mediating difficulty coping predicting seeking professional healthcare
# Regressions
sph ~ dc + ang + COVIDD'

```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare
fitfig23 <-lavaan(modelfig23, ordered = c("st", "k6", "ang", "dc", "uis", "sph", "COVIDP", "COVIDH", "COVIDD", "COVIDDH"), bootstrap = TRUE, data = SEM)
```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare 
summary (fitfig23, fit.measures = TRUE, standardized = TRUE)
```

```{r}
modelfig24 <- '
#Serial Mediation, COVID Delayed Healthcare predicting anger mediating difficulty coping predicting seeking professional healthcare
# Regressions
sph ~ dc + ang + COVIDDH'

```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare
fitfig24 <-lavaan(modelfig24, ordered = c("st", "k6", "ang", "dc", "uis", "sph", "COVIDP", "COVIDH", "COVIDD", "COVIDDH"), bootstrap = TRUE, data = SEM)
```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare 
summary (fitfig24, fit.measures = TRUE, standardized = TRUE)
```

#Stress
```{r}
modelfig25 <- '
#Serial Mediation, COVID Positive predicting stress mediating difficulty coping predicting seeking professional healthcare
# Regressions
sph ~ dc + st + COVIDP'

```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare
fitfig25 <-lavaan(modelfig25, ordered = c("st", "k6", "ang", "dc", "uis", "sph", "COVIDP", "COVIDH", "COVIDD", "COVIDDH"), bootstrap = TRUE, data = SEM)
```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare 
summary (fitfig25, fit.measures = TRUE, standardized = TRUE)
```

```{r}
modelfig26 <- '
##Serial Mediation, COVID Hospitalized predicting stress mediating difficulty coping predicting seeking professional healthcare
# Regressions
sph ~ dc + st + COVIDH'

```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare
fitfig26 <-lavaan(modelfig26, ordered = c("st", "k6", "ang", "dc", "uis", "sph", "COVIDP", "COVIDH", "COVIDD", "COVIDDH"), bootstrap = TRUE, data = SEM)
```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare 
summary (fitfig26, fit.measures = TRUE, standardized = TRUE)
```

```{r}
modelfig27 <- '
#Serial Mediation, COVID Death predicting stress mediating difficulty coping predicting seeking professional healthcare
# Regressions
sph ~ dc + st + COVIDD'

```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare
fitfig27 <-lavaan(modelfig27, ordered = c("st", "k6", "ang", "dc", "uis", "sph", "COVIDP", "COVIDH", "COVIDD", "COVIDDH"), bootstrap = TRUE, data = SEM)
```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare 
summary (fitfig27, fit.measures = TRUE, standardized = TRUE)
```

```{r}
modelfig28 <- '
#Serial Mediation, COVID Delayed Healthcare predicting stress mediating difficulty coping predicting seeking professional healthcare
# Regressions
sph ~ dc + st + COVIDDH'

```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare
f#k6
```{r}
modelfig29 <- '
#Serial Mediation, COVID Positive predicting K6 mediating difficulty coping predicting seeking professional healthcare
# Regressions
sph ~ dc + COVIDP + k6'

```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare
fitfig29 <-lavaan(modelfig29, ordered = c("st", "k6", "ang", "dc", "uis", "sph", "COVIDP", "COVIDH", "COVIDD", "COVIDDH"), bootstrap = TRUE, data = SEM)
```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare 
summary (fitfig29, fit.measures = TRUE, standardized = TRUE)
```

```{r}
modelfig30 <- '
##Serial Mediation, COVID Hospitalized predicting K6 mediating difficulty coping predicting seeking professional healthcare
# Regressions
sph ~ dc + COVIDH + k6'

```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare
fitfig18 <-lavaan(modelfig18, ordered = c("st", "k6", "ang", "dc", "uis", "sph", "COVIDP", "COVIDH", "COVIDD", "COVIDDH"), bootstrap = TRUE, data = SEM)
```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare 
summary (fitfig18, fit.measures = TRUE, standardized = TRUE)
```

```{r}
modelfig19 <- '
#Serial Mediation, COVID Death predicting K6 mediating difficulty coping predicting seeking professional healthcare
# Regressions
sph ~ dc + k6 + COVIDD'

```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare
fitfig4 <-lavaan(modelfig19, ordered = c("st", "k6", "ang", "dc", "uis", "sph", "COVIDP", "COVIDH", "COVIDD", "COVIDDH"), bootstrap = TRUE, data = SEM)
```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare 
summary (fitfig19, fit.measures = TRUE, standardized = TRUE)
```

```{r}
modelfig20 <- '
#Serial Mediation, COVID Delayed Healthcare predicting K6 mediating difficulty coping predicting seeking professional healthcare
# Regressions
sph ~ dc + k6 + COVIDDH'

```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare
fitfig20 <-lavaan(modelfig20, ordered = c("st", "k6", "ang", "dc", "uis", "sph", "COVIDP", "COVIDH", "COVIDD", "COVIDDH"), bootstrap = TRUE, data = SEM)
```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare 
summary (fitfig20, fit.measures = TRUE, standardized = TRUE)
```

#ANGER
```{r}
modelfig100 <- '
#Serial Mediation, COVID Positive predicting anger mediating difficulty coping predicting seeking professional healthcare
# Regressions
sph ~ dc + COVIDP + ang'

```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare
fitfig100 <-lavaan(modelfig100, ordered = c("st", "k6", "ang", "dc", "uis", "sph", "COVIDP", "COVIDH", "COVIDD", "COVIDDH"), bootstrap = TRUE, data = SEM)
```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare 
summary (fitfig100, fit.measures = TRUE, standardized = TRUE)
```

```{r}
modelfig101 <- '
##Serial Mediation, COVID Hospitalized predicting anger mediating difficulty coping predicting seeking professional healthcare
# Regressions
sph ~ COVIDP'

```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare
fitfig101 <-lavaan(modelfig101, ordered = c("st", "k6", "ang", "dc", "uis", "sph", "COVIDP", "COVIDH", "COVIDD", "COVIDDH"), bootstrap = TRUE, data = SEM)
```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare 
summary (fitfig101, fit.measures = TRUE, standardized = TRUE)
```

```{r}
modelfig102 <- '
#Serial Mediation, COVID Death predicting anger mediating difficulty coping predicting seeking professional healthcare
# Regressions
sph ~ dc + COVIDD + ang'

```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare
fitfig102 <-lavaan(modelfig102, ordered = c("st", "k6", "ang", "dc", "uis", "sph", "COVIDP", "COVIDH", "COVIDD", "COVIDDH"), bootstrap = TRUE, data = SEM)
```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare 
summary (fitfig102, fit.measures = TRUE, standardized = TRUE)
```

```{r}
modelfig103 <- '
#Serial Mediation, COVID Delayed Healthcare predicting anger mediating difficulty coping predicting seeking professional healthcare
# Regressions
sph ~ dc + COVIDDH + ang'

```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare
fitfig103 <-lavaan(modelfig103, ordered = c("st", "k6", "ang", "dc", "uis", "sph", "COVIDP", "COVIDH", "COVIDD", "COVIDDH"), bootstrap = TRUE, data = SEM)
```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare 
summary (fitfig103, fit.measures = TRUE, standardized = TRUE)
```

#Stress
```{r}
modelfig103 <- '
#Serial Mediation, COVID Positive predicting stress mediating difficulty coping predicting seeking professional healthcare
# Regressions
sph ~ dc + COVIDP + st'

```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare
fitfig103 <-lavaan(modelfig103, ordered = c("st", "k6", "ang", "dc", "uis", "sph", "COVIDP", "COVIDH", "COVIDD", "COVIDDH"), bootstrap = TRUE, data = SEM)
```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare 
summary (fitfig103, fit.measures = TRUE, standardized = TRUE)
```

```{r}
modelfig104 <- '
##Serial Mediation, COVID Hospitalized predicting stress mediating difficulty coping predicting seeking professional healthcare
# Regressions
sph ~ dc + COVIDH + st'

```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare
fitfig104 <-lavaan(modelfig104, ordered = c("st", "k6", "ang", "dc", "uis", "sph", "COVIDP", "COVIDH", "COVIDD", "COVIDDH"), bootstrap = TRUE, data = SEM)
```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare 
summary (fitfig104, fit.measures = TRUE, standardized = TRUE)
```

```{r}
modelfig105 <- '
#Serial Mediation, COVID Death predicting stress mediating difficulty coping predicting seeking professional healthcare
# Regressions
sph ~ dc + COVIDD + st'

```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare
fitfig105 <-lavaan(modelfig105, ordered = c("st", "k6", "ang", "dc", "uis", "sph", "COVIDP", "COVIDH", "COVIDD", "COVIDDH"), bootstrap = TRUE, data = SEM)
```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare 
summary (fitfig105, fit.measures = TRUE, standardized = TRUE)
```

```{r}
modelfig106 <- '
#Serial Mediation, COVID Death predicting stress mediating difficulty coping predicting seeking professional healthcare
# Regressions
sph ~ dc + COVIDC + st'

```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare
fitfig106 <-lavaan(modelfig106, ordered = c("st", "k6", "ang", "dc", "uis", "sph", "COVIDP", "COVIDH", "COVIDD", "COVIDDH"), bootstrap = TRUE, data = SEM)
```

```{r}
#Run the Med model, Difficulty coping mediating k6 and seeking professional healthcare 
summary (fitfig106, fit.measures = TRUE, standardized = TRUE)
```






